\documentclass[letterpaper]{letter}
\usepackage{amssymb,lmodern,enumitem,tabto}
\usepackage[margin=1in, top=0.8in, bottom=0.8in]{geometry}

\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}

\begin{document}
\large

\begin{center}
\Huge
BRCH3 Ice Run Instructions
\end{center}

\begin{center}
(things don't go smoothly, just improvise as necessary)
\end{center}

\begin{enumerate}
  \item Either MUG or one of the shift members will have the cash pouch, which holds the cash/credit card needed to buy the ice.
  \item Arrive on shift around 12:00pm, and find the megaphone and wagons. Call 'Ice Run' on the megaphone, and give the camp 5 minutes to get the last orders in. If people need to change or cancel pre-orders, make a note on the spreadsheet.
  \item Grab the clipboard and bike wagon, and get in line at the 9 o'clock Arctica. While in line, count up the the bags of crushed and block ice needed. Verify there is enough cash from today's and previous days' orders plus \$200 cash for change. USE THE CC TO PAY.
  \item Get back to camp, announce that you guys are back on the megaphone, and deliver the ice to the coolers for any \emph{absent/occupied} camp members. Check off that each bag is delivered on the spreadsheet. Make a note of how much cash should be in the pouch.
  \item Designate someone to hand off the cash pouch to someone on the next shift.
\end{enumerate}

\vspace*{0.1cm}

\begin{center}
  \Huge
  Ice Runner Daily Schedule
  \large
  \begin{description}[leftmargin=9cm, labelsep=4em, style=multiline, labelindent=3cm]
    \item[Early Entry] MUG \& helper
    \item[Monday] Anal Beaching \& Just Chairman
    \item[Tuesday] MUG \& Seaman
    \item[Wednesday] Geordi La Foreskin \& Seaman
    \item[Thursday] Hold Whore \& T-Ball 
    \item[Friday] Brut Force \& Just Reg 
    \item[Saturday] Scrum \& DFAU
    \item[Sunday] MUG \& helper
    \item[Monday] You're on your own       
\end{center}

\vspace*{0.1cm}

\begin{center}
  \Huge 
  Ice Schedule and Locations
  \large
  \begin{description}[leftmargin=9cm, labelsep=4em, style=multiline, labelindent=2cm]
  % [labelsep=4em, align=center]
    \item[Early entry \hspace{220pt} Thursday - Sunday 12-6pm] Camp Arctica: Center Camp
    \item[] 
    \item[] 
    \item[Burn week \hspace{220pt} Monday - Sunday 9am-6pm] Ice-9: 9:00 Portal (9:00 \& G)\\Camp Arctica: Center Camp\\Ice Cubed: 3:00 Portal
    \item[] 
    \item[Labor Day \hspace{220pt} Monday 9am-12pm] Ice-9: 9:00 Portal (9:00 \& G)\\Camp Arctica: Center Camp\\Ice Cubed: 3:00 Portal
  \end{description}
\end{center}

\end{document}
